Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2022-08-28 response_to_decision_letter.tex

\documentclass[11pt]{article}
\usepackage{xcolor}
\begin{document}

\textbf{Response to Review for Manuscript Number: SIM-22-0426}

Title: "Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays"

We are grateful to the editor and reviewers for their thoughtful comments and the opportunity to improve and resubmit our manuscript.
Our response to individual comments from each reviewer follow.

\textbf{Reviewer: 1}
(There are no comments.)

\textbf{Reviewer 2}

\begin{itemize}
    \item \textbf{This paper has many strengths and yet could benefit from a revision that clarifies the main contribution(s) of the work. The new method is mathematically clever and appears to have the nice property of guaranteeing nominal CI coverage (though it is unclear if this has been rigorously proved); the contribution alone of generalizing the melded CI to more than 2 parameters is interesting, as well as the applicability of their method to complex surveys where each individual has their own weight. There was clearly painstaking detail taken in simulation studies to evaluate the new method.}

    \item \textbf{The abstract and introduction imply that a main contribution of the work is that the new methods have better properties in simulations, and no drawbacks are hinted at. However, it is not clear that the new methods achieved better performance. Performance is strong at very low prevalences, but fades at higher prevalences. This is probably because the gamma CI method uses a Poisson approximation to the binomial that assumes a small binomial parameter, i.e., a small prevalence closer to 0 than 1.}

    \textbf{“our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage” (Abstract).}

    \textbf{“we…show through simulations that [our new method] beats the best of [the established frequentist competitors] in each of the three stages **with respect to guaranteeing coverage**” (Introduction, last paragraph; emphasis added.) The three stages are (1) random samples with misclassification; (2) weighted samples without misclassification (using a perfect assay); and (3) weighted samples with misclassification.}

    We have added some mentions in the text about the drawbacks to our proposed methods and clarify the scenarios when our methods are shown to be superior:

    Abstract:
    ``We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low. In other settings, our methods are shown to be overly conservative."

    Introduction:

    ``However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage."

    Discussion:
    ``These new confidence intervals appear to guarantee coverage in most simulated settings, including some scenarios where competitor methods dramatically under-cover.
    In general, our methods demonstrate higher coverage than competitor methods in most scenarios, sometimes being very conservative while competitor methods demonstrate closer to nominal coverage.""

    \item \textbf{The new method may guarantee coverage well, but it seems to do so by using conservative intervals that over-cover. Should such intervals be preferred to intervals that are more permissive (anti-conservative)?}

    \textcolor{red}{Mike, can you add any comments about this?}

    \item \textbf{For Stage 1 (Sections 2.2/3.1), consider Figure 1. The text states that “both [our new and the existing Lang-Reiczigel] methods achieve approximately nominal coverage, with the melding method being somewhat more conservative.” This definition of “approximately nominal” is debatable; the figure shows that the existing Lang-Reiczigel method achieves nominal 95\% coverage in most situations, while the melding method usually over-covers.}

    We have updated the text to more accurately reflect the simulation results:

    ``Figure~1 shows that, when specificity is less than perfect, the Lang-Reiczigel method achieves approximately nominal coverage, while the melding method is slightly more conservative, generally demonstrating 96\%-97\% coverage with 95\% confidence intervals."

    \item \textbf{(The discussion of lower and upper error probabilities in Section 3.1 is similar. The authors criticize the Lang-Reiczigel intervals for having “lower error above 2.5\%, which is undesirable…”. However, neither the lower nor upper errors of the melding method achieves nominal 2.5\% in any scenario. This is undesirable and unremarked upon. As a minor point, no reason for focusing on lower and upper error probabilities is stated; those Figures may be better relegated to the appendices.)}

    We have updated the text to motivate the figures and remark upon the undesirable lower error properties of the melding method:

    ``For a more nuanced depiction of each method's properties, we separate the overall coverage into lower and upper errors.
    Figure~3 shows that both methods make upper errors with roughly the same frequency.
    Figure~2 demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%.
    Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
    For applications in which there is a need to bound the lower errors, the melding method is superior."

    \item \textbf{For Stage 2 (Sections 2.3/3.2), Figures 4-5 display scenarios where prevalence is 0.5\%, and the new wsPoisson method generally performs well compared to competitors. However, the competitor methods demonstrate almost uniformly better properties (coverage closer to nominal) than the authors’ wsPoisson method when prevalence is 5\% in Figures 6-7. This is not pointed out in the textual description in the last paragraph of Section 3.2}

    We have updated the text to reflect this observation:
    ``In scenarios with higher overall prevalence, the Agresti-Coul and Korn-Graubard methods achieve close to nominal coverage, while the wsPoisson method strongly over-covers."

    \item \textbf{For Stage 3 (Sections 2.4/3.3), the only comparator shown in the Figures is the WprevSeSp Binomial developed in the Kalish et al. paper (despite the text saying wsPoisson was also compared). Again, the textual description belies the results in the Figures. While there are some scenarios in Figures 8-11 where the WprevSeSp Binomial interval under-covers dramatically, most scenarios appear to show that binomial interval having consistently closer-to-nominal coverage compared to the over-covering WprevSeSp Poisson.}

    In our simulations, we did compare the wsPoisson method to the two melding methods, but the results were poor and made comparison between the melding methods more difficult to observe in the figures.
    We have clarified this point in the text.
    We have also noted the generally superior performance of the WprevSeSp Binomial method:

    ``In the other scenarios tested, the WprevSeSp Binomial generally achieves closer to nominal coverage than the WprevSeSp Poisson."

    \item \textbf{Is there a substantive reason that the prevalences assessed in simulations are 0.5\% and 5\%? While the number of scenarios evaluated are clearly substantial, it would be interesting to understand the methods’ performance across a larger portion of the [0, 1] prevalence parameter space.}

    We only evaluated 0.5\% and 5\% because the greater prevalence leads to over-coverage for our methods.
    We have updated the text to point to this drawback throughout.

    \item If the main contribution of the paper is superior coverage properties, then the above issues of the Poisson approximation assuming a small prevalence as well as simulation results and interpretation should be addressed. The authors could instead elaborate on other contributions of the work detailed above.

    \item Minor issues:

    \begin{itemize}
        \item \textbf{2.2 Line 23-24: “where we define 0/0” seems unusual when this is typically taken as an indeterminate value. Clarify what is meant? The estimator in Equation 5 seems to be the Rogan-Gladen (1978) estimator with truncation in cases when the estimator falls outside the parameter range of [0, 1]?}

        We have adjusted the definition of the estimator to avoid defining 0/0 = 0. It is now presented as
        \begin{equation}
        \hat{\beta}^* \equiv 
        g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
        \equiv 
        \left\{ 
        \begin{array}{ll}
        1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
        \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
        \mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
        0 & \mbox{ otherwise.} 
        \end{array}
        \right.
        \end{equation}

        \item \textbf{2.2 Lines 24-32: It would be helpful for the unfamiliar reader to include more background on the melding method. For instance, what exactly is the definition of the confidence distribution? Why are the confidence distributions Beta for a binomial experiment?}

        I have added the definition of the confidence distribution to section 2.2
        \textcolor{red}{Mike, feel free to add more context/intution.}

        \item \textbf{As a formatting note, the paper could be much more concise if (a) many of the figures were moved to appendices, and (b) fewer lines are used for equations, e.g., the definition of the Lang-Reiczigel interval in Section 2.2.}

        We have adjusted the presentation of Section 2.2 to reduce the lines used.

        \item \textbf{Please elaborate on why the third equality in Section 2.5.2, p. 8, lines 17-25 (variance of  beta-hat) holds.}

        The referenced equation is reproduced here:
        \begin{eqnarray*}
        \textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
        \end{eqnarray*}

        The third equality holds because \( \textrm{var}_P( I_{ij}) = P_j \) and \( Y_j^2= Y_j \), because \( Y_j \) is binary.

        We have clarified this in the text:

        \begin{eqnarray*}
        \textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
        \end{eqnarray*}

        \item \textbf{There are several typographical errors that distract the reader. The manuscript should be reread with this attention to detail in mind. Some instances: 2.3 Line 52: “the wsPoison method”; Section 5: “Further worked is needed”; the inconsistency about the assessment of wsPoisson in the simulations; etc.}

        \textcolor{red}{Damon: I fixed these errors and a few more. Mike and Barry should also take a look for proofreading.}

    \end{itemize}
\end{itemize}

\end{document}

### 2022-08-28 PrevAdjSurvey.tex
Updates from Overleaf

\documentclass[AMA,STIX1COL]{WileyNJD-v2}
\usepackage{moreverb}

\DeclareMathOperator{\Var}{Var}

@@

\begin{document}

\title{Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays}

@@

\abstract[Abstract]{We present several related methods for creating confidence intervals to assess disease prevalence in variety of survey sampling settings. These include simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests, with the first two settings considered special cases of the third. Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals. We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage. We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}

@@

In simulations we compare our method to established frequentist competitors.
and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage. 
We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
The exact method of DiCiccio, et al \cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive'', and it has not been applied to surveys using post-stratification weighting. In contrast, our new method can very tractable in those situations.

@@

\begin{equation}
\hat{\beta}^* \equiv 
g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
\equiv 
\left\{ 
\begin{array}{ll}
1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
\mbox{ if $\hat{\phi}_p \geq \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
0 & \mbox{ otherwise} 
\end{array}
\right.
\label{eq:srs-beta-est}
\end{equation}
where we define $0/0=0$.
% Damon, that definition is arbitrary, it is just used so that everything is defined

To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \). Confidence distributions are like frequentist posterior distributions\cite{Xie2013}.
The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{Fay2021}.

@@

\begin{equation*}
    d\beta = 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}
\end{equation*}

\begin{equation*}
    \Var(\beta_1^{*\prime}) = \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
\end{equation*}

\begin{equation*}
    m_p^\prime = m_p +2
\end{equation*}

\begin{equation*}
    m_n^\prime = m_n + 2
\end{equation*}

\begin{equation*}
    \phi_p^\prime = \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2}
\end{equation*}

\begin{equation*}
   1 - \phi_n^\prime = \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} 
\end{equation*}

\begin{equation*}
   \beta_1^{*\prime} = \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} 
\end{equation*}
and 
\begin{equation*}
    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}.
\end{equation*}

@@

\begin{equation*}
    G_{\beta^*}^L \sim \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right)
\end{equation*}

\begin{equation*}
    G_{\beta^*}^U \sim \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right)
\end{equation*}

\begin{equation*}
    y = \sum_{i=1}^K \frac{w_i}{n_i} x_i
\end{equation*}

\begin{equation*}
    v = \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i
\end{equation*}

\begin{equation*}
    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right)
\end{equation*}

\begin{equation*}
    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
\end{equation*}

We call this the wsPoison method, since it assumes a weighted sum of Poissons.
We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
Dean and Pagano showed in simulations that the standard Wald interval had poor coverage with low prevalence (e.g., Fig. 1 of that paper showed 95\% confidence intervals with coverage of less than 85\% for prevalence values less than 2\%).
Since the confidence interval of Rosin, et al \cite{rosin2021estimating} reduces to the Wald interval with perfect assays, we will not include that method in the simulation comparisons.

@@

\begin{equation*}
   \tilde{x} = \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c 
\end{equation*}

\begin{equation*}
   \tilde{n} = n_{\text{eff}} + 2c 
\end{equation*}

\begin{equation*}
    \tilde{p} = \tilde{x} / \tilde{n}
\end{equation*}

\begin{equation*}
   c = q_Z^2/2
\end{equation*}

@@

where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
\begin{equation*}
    % B^L_{KG} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
    B^L_{KG} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
\end{equation*}

\begin{equation*}
    % B^U_{KG} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
    B^U_{KG} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
\end{equation*}

@@

For this paper we define the weights differently, because we want to model our estimator as a weighted sum of Poisson random variables.
Thus, we use $w_i = 1/(nNp_i)$ and $W_j= 1/(nNP_j)$ so that the sums have expectation $1$.
In the complex survey case,
we start with the independent multinomial model as in equation~\ref{eq:betahatMultinomial}, then we use the relationship between the multinomial and Poisson distributions.
Using the ``multinomial-Poisson transformation'', the maximum
likelihood estimates (MLE) for a multinomial random variable are equivalent to the MLEs for independent Poisson random variables, and
the variances are asymptotically equivalent (see Baker\cite{Baker:1994}).
Even though we model $\hat{\beta}$ using multinomial random variables where there are many missing values (which occurs in our situation whenever $I_{ij}=0$),
that multinomial-Poisson relationship holds even when there are missing variables (see Baker\cite{Baker:1994}, Section 3).
For both the Poisson and multinomial models, $E(I_{ij}) = P_j$, and $\hat{\beta}$ is unbiased under either model.
For the Poisson model, all the $I_{ij}$ are independent and each mean equals its variance, so that the variance of $\hat{\beta}$ under this model is
\begin{eqnarray*}
\textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
\end{eqnarray*}
We estimate $\textrm{var}_P \left(\hat{\beta} \right)$ by multiplying each term in the sum by $I_{ij}/P_j$, which has an expectation of $1$ and eliminates terms of non-selected individuals, giving
\begin{eqnarray}
\widehat{\textrm{var}}_P \left(\hat{\beta} \right)
& = &   \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{n^2 N^2 P_j^2}  =  \sum_{i=1}^{n}  \frac{  y_i}{n^2 N^2 p_i^2} \label{eq:hatvarbetahat1}
\end{eqnarray}
Under the Poisson model $\widehat{\textrm{var}}_P \left(\hat{\beta} \right)$ is an unbiased estimator of $\textrm{var}_P \left(\hat{\beta} \right)$.

@@

Figure~\ref{fig:coverage_comparison_plot} shows that, when specificity is less than perfect, both methods achieve approximately nominal coverage, with the melding method being somewhat more conservative.
When specificity is 100\%, both methods are conservative.
Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%, which is undesirable for applications for which there is a need to bound the lower errors.

@@

From Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}, we note that the two competitor methods generally exhibit lower coverage as the coefficient of variation among the weights increases.
In Figure~\ref{fig:perfect_coverage_50_groups_0_005_prev}, this coverage falls below 60\% when the prevalence very low and is concentrated among the highest weights, and the coefficient of variation among the weights exceeds 4.
Uniform distribution of prevalence among the weights, increased overall prevalence, and larger sample sizes among fewer groups all appear to lessen the severity of this problem.
In contrast, the wsPoisson method appears to guarantee coverage in all scenarios. The wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases, when the other methods can have problems guaranteeing coverage. 
In all cases, the wsPoisson method is more conservative than the competitor methods.
This is similar to the behavior observed in Fay and Feuer\cite{FayF:1997}, where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:perfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}.
In scenarios where coefficient of variation among the survey weights is high, the wsPoisson intervals are often two or three times wider than intervals produced by competing methods.

>>>>

\documentclass[AMA,STIX1COL]{WileyNJD-v2}
\usepackage{moreverb}
\usepackage{pdfpages}
\DeclareMathOperator{\Var}{Var}

@@

\begin{document}
\includepdf{pub_form-coversheet-peer_reviewed-2.pdf}
\title{Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays}

@@

\abstract[Abstract]{We present several related methods for creating confidence intervals to assess disease prevalence in variety of survey sampling settings. These include simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests, with the first two settings considered special cases of the third. Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals. We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low. In other settings, our methods are shown to be overly conservative. We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}

@@

In simulations we compare our method to established frequentist competitors and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage.
However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage.
We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
The exact method of DiCiccio, et al \cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive'', and it has not been applied to surveys using post-stratification weighting. In contrast, our new method can very tractable in those situations.

@@

\begin{equation}
\hat{\beta}^* \equiv 
g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
\equiv 
\left\{ 
\begin{array}{ll}
1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
\mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
0 & \mbox{ otherwise.} 
\end{array}
\right.
\label{eq:srs-beta-est}
\end{equation}
% Damon, that definition is arbitrary, it is just used so that

To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \). Confidence distributions are frequentist estimators of a parameter, which can be used similarly to the bootstrap or posterior distributions. Formally, a confidence distribution is a function \(H_{n}(\cdot)=H_{n}(\mathbf{x}, \cdot)\) on \(\mathcal{X} \times \Theta \rightarrow[0,1]\), where \( \Theta \) is the parameter space of the parameter of interest (\( \theta \)) and \( \mathcal{X} \) is the sample space corresponding to sample data \(\mathbf{x}=\left\{x_{1}, \ldots, x_{n}\right\}\), which has two properties: (i) For each \(\mathbf{x} \in \mathcal{X}, H_{n}(\cdot)\) is a cumulative distribution function on \(\Theta \). (ii) At the true parameter value \(\theta=\theta_{0}, H_{n}\left(\theta_{0}\right) \equiv H_{n}\left(\mathbf{x}, \theta_{0}\right)\), as a function of the sample \(\mathbf{x}\), follows the uniform distribution \(U[0,1]\) \cite{Xie2013}.

The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{Fay2021}.

@@

\begin{align*}
    d\beta =& 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}\\
    \Var(\beta_1^{*\prime}) =& \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
\end{align*}

\begin{align*}
    m_p^\prime =& m_p +2 &
    m_n^\prime =& m_n + 2 \\
    \phi_p^\prime =& \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2} &
   1 - \phi_n^\prime =& \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} \\
   \beta_1^{*\prime} =& \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} &
    \beta_1^\prime =& \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}.
\end{align*}

@@

\begin{align*}
    G_{\beta^*}^L \sim& \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right) &
    G_{\beta^*}^U \sim& \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right) \\
    y =& \sum_{i=1}^K \frac{w_i}{n_i} x_i &
    v =& \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i \\
    y^* =& y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) &
    v^* =& v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
\end{align*}

We call this the wsPoisson method, since it assumes a weighted sum of Poissons.
We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
Dean and Pagano showed in simulations that the standard Wald interval had poor coverage with low prevalence (e.g., Fig. 1 of that paper showed 95\% confidence intervals with coverage of less than 85\% for prevalence values less than 2\%).
Since the confidence interval of Rosin, et al \cite{rosin2021estimating} reduces to the Wald interval with perfect assays, we will not include that method in the simulation comparisons.

@@

\begin{align*}
   \tilde{x} =& \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c &
   \tilde{n} =& n_{\text{eff}} + 2c \\
    \tilde{p} =& \tilde{x} / \tilde{n} &
   c =& q_Z^2/2
\end{align*}

@@

where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
\begin{align*}
    % B^L_{KG} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
    B^L_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right) &
    % B^U_{KG} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
    B^U_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
\end{align*}

@@

For this paper we define the weights differently, because we want to model our estimator as a weighted sum of Poisson random variables.
Thus, we use $w_i = 1/(nNp_i)$ and $W_j= 1/(nNP_j)$ so that the sums have expectation $1$.
In the complex survey case,
we start with the independent multinomial model as in equation~\ref{eq:betahatMultinomial}, then we use the relationship between the multinomial and Poisson distributions.
Using the ``multinomial-Poisson transformation'', the maximum
likelihood estimates (MLE) for a multinomial random variable are equivalent to the MLEs for independent Poisson random variables, and
the variances are asymptotically equivalent (see Baker\cite{Baker:1994}).
Even though we model $\hat{\beta}$ using multinomial random variables where there are many missing values (which occurs in our situation whenever $I_{ij}=0$),
that multinomial-Poisson relationship holds even when there are missing variables (see Baker\cite{Baker:1994}, Section 3).
For both the Poisson and multinomial models, $E(I_{ij}) = P_j$, and $\hat{\beta}$ is unbiased under either model.
For the Poisson model, all the $I_{ij}$ are independent and each mean equals its variance, so that the variance of $\hat{\beta}$ under this model is
\begin{eqnarray*}
\textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j}{n^2 N^2 P_j^2}  \\
& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
\end{eqnarray*}
We estimate $\textrm{var}_P \left(\hat{\beta} \right)$ by multiplying each term in the sum by $I_{ij}/P_j$, which has an expectation of $1$ and eliminates terms of non-selected individuals, giving
\begin{eqnarray}
\widehat{\textrm{var}}_P \left(\hat{\beta} \right)
& = &   \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{n^2 N^2 P_j^2}  =  \sum_{i=1}^{n}  \frac{  y_i}{n^2 N^2 p_i^2} \label{eq:hatvarbetahat1}
\end{eqnarray}
Under the Poisson model $\widehat{\textrm{var}}_P \left(\hat{\beta} \right)$ is an unbiased estimator of $\textrm{var}_P \left(\hat{\beta} \right)$.

@@

Figure~\ref{fig:coverage_comparison_plot} shows that, when specificity is less than perfect, the Lang-Reiczigel method achieves approximately nominal coverage, while the melding method is slightly more conservative, generally demonstrating 96\%-97\% coverage with 95\% confidence intervals.
When specificity is 100\%, both methods are very conservative, achieving nearly 100\% coverage.
For a more nuanced depiction of each method's properties, we separate the overall coverage into lower and upper errors.
Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%.
Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
For applications in which there is a need to bound the lower errors, the melding method is superior.

@@

From Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}, we note that the two competitor methods generally exhibit lower coverage as the coefficient of variation among the weights increases.
In Figure~\ref{fig:perfect_coverage_50_groups_0_005_prev}, this coverage falls below 60\% when the prevalence very low and is concentrated among the highest weights, and the coefficient of variation among the weights exceeds 4.
Uniform distribution of prevalence among the weights, increased overall prevalence, and larger sample sizes among fewer groups all appear to lessen the severity of this problem.
In contrast, the wsPoisson method appears to guarantee coverage in all scenarios.
The wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases, when the other methods can have problems guaranteeing coverage. 
In all cases, the wsPoisson method is more conservative than the competitor methods.
In scenarios with higher overall prevalence, the Agresti-Coul and Korn-Graubard methods achieve close to nominal coverage, while the wsPoisson method strongly over-covers.
This is similar to the behavior observed in Fay and Feuer\cite{FayF:1997}, where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:perfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}.
In scenarios where coefficient of variation among the survey weights is high, the wsPoisson intervals are often two or three times wider than intervals produced by competing methods.
